`SCPCL000824` - Using `SingleR` for classification of tumor cells

### 2024-07-23 analyses/cell-type-ewings/exploratory_analysis/annotation_notebooks/SCPCS000492/SCPCL000824_singler-classification.Rmd
Fix spelling errors

- There seems to be mostly consensus across all four methods on which cells are tumor cells, which is consistent with the upset plot. 
- When only using Blueprint, a lot of cells are categorized as "Normal". 
This means they match the non-tumor cells identified in `SCPCL000822` more than they match the normal cell types in the `Blueprint` reference. 
Additionally, with only Blueprint, there is a group of cells that are called as tumor but actually appear to match endothelial cells present in `SCPCL000822`.
- The cells that aren't called as either Tumor or Normal in the Blueprint only reference mostly match up to `erythrocyte` in the reference that just uses `SCPCL000822` (original). 
These same cells match to their corresponding Blueprint cell type when combining `SCPCL000822` and Blueprint (e.g., fibroblasts, neurons, and epithelial cells are identiied in both). 
- When comparing using just `SCPCL000822` (original) to `SCPCL000822` and Blueprint (original and blueprint), we see an overlap in endothelial cells and chondrocytes. 
We also see that for the most part the top cell types identified are the same except when using blueprint you see the addition of epithelial cells. 
- Using tumor only appears to label some cells as tumor that are labeled as normal with other methods. 
For example, comparing tumor only to both original and original and blueprint shows that tumor cells are classified as endothelial cells using either of the other two methods.

>>>>

- There seems to be mostly consensus across all four methods on which cells are tumor cells, which is consistent with the upset plot. 
- When only using Blueprint, a lot of cells are categorized as "Normal". 
This means they match the non-tumor cells identified in `SCPCL000822` more than they match the normal cell types in the `Blueprint` reference. 
Additionally, with only Blueprint, there is a group of cells that are called as tumor but actually appear to match endothelial cells present in `SCPCL000822`.
- The cells that aren't called as either Tumor or Normal in the Blueprint only reference mostly match up to `erythrocyte` in the reference that just uses `SCPCL000822` (original). 
These same cells match to their corresponding Blueprint cell type when combining `SCPCL000822` and Blueprint (e.g., fibroblasts, neurons, and epithelial cells are identified in both). 
- When comparing using just `SCPCL000822` (original) to `SCPCL000822` and Blueprint (original and blueprint), we see an overlap in endothelial cells and chondrocytes. 
We also see that for the most part the top cell types identified are the same except when using blueprint you see the addition of epithelial cells. 
- Using tumor only appears to label some cells as tumor that are labeled as normal with other methods. 
For example, comparing tumor only to both original and original and blueprint shows that tumor cells are classified as endothelial cells using either of the other two methods.
